%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Author:
% Ravi Varma (https://ravivarmathotakura.github.io/portfolio/)
% 
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}
\hypersetup{%
    pdfborder = {0 0 0}
}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\namesection{Ravi}{Varma}{ % Your name profile or other web address
\href{https://ravivarmathotakura.github.io/portfolio/}{\bf https://ravivarmathotakura.github.io/portfolio/} \\
\href{mailto:ravivarmathotakura@gmail.com}{ravivarmathotakura@gmail.com} | (+91)9035528281 % Your contact information
}

%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\subsection{Programming}
Python, R, SQL \\
Unix, LaTex, HTML \\
%JavaScript (D3.js), HTML, and CSS \\

\sectionspace % Some white space after the section

\subsection{Machine Learning}
%Regression \\
%Support Vector Machines \\
%Naive Bayes \\
%K-Nearest Neighbors \\
%Decision Trees \\
%Cluster Analyses \\
Natural Language Processing \\
Deep Learning \\
Feature Engineering \\
Data Cleansing \\

\sectionspace % Some white space after the section

\subsection{Framework}
Scikit-Learn, TensorFlow \\
Keras, Pytorch, Matplotlib \\
Pandas, Numpy, Seaborn, Django \\

\sectionspace % Some white space after the section

\subsection{Tools}
Jupyter, Tableau \\
%PostgreSQL and PostGIS \\
AWS, Github \\
%Spark and Hadoop \\
%MongoDB \\
%QGIS \\
%CartoDB \\
%MapBox \\


\sectionspace % Some white space after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\subsection{Master of Computer Application (M.C.A)}
\descript{JNTU Kakinada University}
\location{2007-2010 | AP, India
}

\sectionspace % Some white space after the section

%------------------------------------------------

\subsection{B.Com Computers}
\descript{Andhra University}
\location{2004-2007 | AP, India
}

\sectionspace % Some white space after the section


%------------------------------------------------
% Links
%------------------------------------------------

\section{Links} 

Github:// \href{https://github.com/ravivarmathotakura}{\bf ravivarmathotakura} \\
LinkedIn:// \href{https://www.linkedin.com/in/ravivarmathotakura/}{\bf ravivarmathotakura}

\sectionspace % Some white space after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the left column
\hfill
%
%----------------------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------------------
%
\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

\runsubsection{Dynamic Cancer Care Pvt Ltd, Healthcare Startup}
\descript{| Data Scientist \& Founder}

\location{Jan 2016 – Sept 2019 | Hyderabad, India}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item {Built a competent team from scratch as a startup company.}
\item {Product Design and Prototyping.}
\item {Collaborated with team to develop an internal tool that automates the creation of verified users.}
\item {Create reports based on findings to be presented to executives at monthly board meeting, making recommendations for improvement
in addition to raw information.}
\item {Researched new technology for our field, as well as new operational strategies, making recommendations for implementation.}
\item {Auto classification of health care documents like prescription, doctor notes and health reports.}
\item {Built a chatbot using Rasa framework which interacts with users and helps them to find a oncologist and cancer related queries.}
\item {Auto classification of health care documents like prescription, doctor notes and health reports.}
\item {Cancer Treatment Plan recommendations based on diagnosis.}


\end{tightitemize}

\sectionspace % Some white space after the section

%------------------------------------------------

\runsubsection{Sonata Software}
\descript{| SENIOR DATA ANALYST}
\location{Feb 2017 – Apr 2018 | Bengaluru \& Hyderabad, India}
\begin{tightitemize}
\item {Interacting with the Business Teams for requirements gathering, design and implementing SAP BODS jobs based on project plan.}
\item {Responsible for specifications, implementations and analytics.}

\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{IBM India}
\descript{| DATA ANALYST}
\location{Jan 2015 – Jul 2015 | Bengaluru, India}
\begin{tightitemize}
\item {Involved in the development and implementation of the Enterprise Data ware housing.}
\item {Building MS SQL Server Jobs based on the business requirement and responsible for application deployment and release.}
\item {Involved in an Architectural, Technical and Sprint design.}
\end{tightitemize}
\sectionspace % Some whitespace after the section

\runsubsection{SchoolCity Learning India Pvt Ltd}
\descript{| SOFTWARE ENGINEER}
\location{Aug 2011 – Jun 2014 | Bengaluru, India}
\begin{tightitemize}
\item {Developed ETL packages to validate, extract, transform and load data to data warehouse.}
\item {Handling the MS SQL Server Jobs and working on troubleshooting.}
\item {Preparing the Technical Specification documents and Conducting scrum meetings.}
\end{tightitemize}
\sectionspace % Some white space after the section

%----------------------------------------------------------------------------------------

\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}