%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

%\cventry
%{Data Scientist \& Machine Learning Engineer} % Job title
%{Self Directed - Independent} % Organization
%{Visakhapatnam, India} % Location
%{Jan. 2020 - Exp. Present} % Date(s)
%{ % Description(s) of tasks/responsibilities
%\begin{cvitems}
%\item {}
%\item {}
%\item {}
%\end{cvitems}
%}

%------------------------------------------------

\cventry
{Data Scientist \& Founder} % Job title
{Dynamic Cancer Care Pvt Ltd, Healthcare Startup} % Organization
{Hyderabad, India} % Location
{Jan. 2016 - Exp. Sept. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Built a competent team from scratch as a startup company.}
\item {Product Design and Prototyping.}
\item {Collaborated with team to develop an internal tool that automates the creation of verified users.}
\item {Create reports based on findings to be presented to executives at monthly board meeting, making recommendations for improvement in addition to raw information.}
\item {Researched new technology for our field, as well as new operational strategies, making recommendations for implementation.}
\item {Auto classification of health care documents like prescription, doctor notes and health reports.}
\item {Built a chatbot using Rasa framework which interacts with users and helps them to find a oncologist and cancer related queries.}
\item {Auto classification of health care documents like prescription, doctor notes and health reports.}
\item {Cancer Treatment Plan recommendations based on diagnosis.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Senior Data Analyst} % Job title
{Sonata Software} % Organization
{Bengaluru \& Hyderabad, India} % Location
{Feb. 2017 - Apr. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Interacting with the Business Teams for requirements gathering, design and implementing SAP BODS jobs based on project plan.}
\item {Responsible for specifications, implementations and analytics.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Data Analyst} % Job title
{IBM India} % Organization
{Bengaluru, India} % Location
{Jan. 2015 - Jul. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Involved in the development and implementation of the Enterprise Data ware housing.}
\item {Building MS SQL Server Jobs based on the business requirement and responsible for application deployment and release.}
\item {Involved in an Architectural, Technical and Sprint design.}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{SchoolCity Learning India Pvt Ltd} % Organization
{Bengaluru, India} % Location
{Aug. 2011 - Jun. 2014} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed ETL packages to validate, extract, transform and load data to data warehouse.}
\item {Handling the MS SQL Server Jobs and working on troubleshooting.}
\item {Preparing the Technical Specification documents and Conducting scrum meetings.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}